---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ecopiapi

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of ecopiapi is to Get, post, patch data from the ecop API.

## Installation

You can install the development version of ecopiapi from [GitHub](https://github.com/) with:
You will need your Github PAT for authentication (privat repo).

``` r
# install.packages("devtools")
devtools::install_github("OekoFor/ecopiapi", auth_token = {GITHUB_PAT})
```

Install a specific version
```r
devtools::install_github("OekoFor/ecopiapi@0.0.9", auth_token = {GITHUB_PAT})
```

## Example

To interact with the API, you need a valid key.
It is recommended to store it as an environmental variable in '.Renviron' in the root directory of th project.
The envar must be named 'ECOPI_API_KEY'.

```{r example, eval=FALSE}
library(ecopiapi)
get_detections_list(params = list("project_name" = "017_neeri", "datetime__month" = 3))
get_latest_detections()
get_latest_detections_by_project(project_name = "017_neeri")
get_latest_detections_by_recorder(recorder_name = "00000000d76d0bf9")
get_latest_detections_by_recordergroup(project_name = "053_sion", recordergroup_name = "lapwing")
get_recordings_list(params = list("project_name" = "017_neeri", "datetime__month" = 3))

```
